---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Social Parameter Recovery
```{r setup-asoc-parrecov, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, results = 'markup', warning = TRUE)

library(knitr)
library(dplyr)
library(tidyr)
library(purrr)
library(tibble)
library(stringr)

library(ggplot2)
library(ggpubr)
library(viridis)
library(ggdist)

library(rstan)
library(tidybayes)
library(bayesplot)
library(randtoolbox)

setwd("~/Users/MarienhagenJonathan/rlforaging")

source("asocial/code/functions/softmax.R")
source("asocial/code/functions/diagnostics.plot.R")
source("asocial/code/functions/plot.par.recov.R")
source("asocial/code/functions/getmodels.R")
source("asocial/code/functions/m1.1.fixed.sim.R")
source("asocial/code/functions/m2.1.fixed.sim.R")
source("asocial/code/functions/m3.1.fixed.sim.R")
source("asocial/code/functions/m4.1.fixed.sim.R")
source("asocial/code/functions/m4.2.fixed.sim.R")
source("asocial/code/functions/m4.3.fixed.sim.R")



```
```{r, directories, include=FALSE}
if(!dir.exists("asocial/results")){dir.create("asocial/results")}
if(!dir.exists("asocial/results/parrecov")){dir.create("asocial/results/parrecov")}
if(!dir.exists("asocial/results/parrecov/diagnostics")){dir.create("asocial/results/parrecov/diagnostics")}

```

## Model
The parameter recovery was run for the model that won the model comparison.
```{r, model-asoc-parrecov, echo=TRUE, results='markup'}

# Load winning model
load(file = paste("asocial/results/modelcomp", "modelcomp.Rdata", sep = "/"))
remove(results, comparison, comparison.named)

# Parse name
winner = gsub(pattern = ".hierarch", "", winner)

# Get list of models
models = getmodels(hierarch = FALSE) # Parameter recovery with fixed effects versions

# Index winning model in list
models = lapply(models, function(x) x[which(models$name == winner)])

# Set model index for later
if(length(models$name) == 1){mod = 1}else{warning("Your list of winning models contains more than one model. Something went wrong!")}
```

## Synthetic Data
The parameter recovery was performed by first simulating synthetic datasets and 
then fitting to winning model to this synthetic data. Each of the nsim number
of simulations used a different combination of generating parameters, but was
generated using the following synthetic experiment.
```{r, experiment-asoc-parrecov, echo = T, results='markup'}
# Number of simulated experiments
nsim=10

# Experimental parameters (identical for all simulations)
exp.pars = list(
  sessions = 18,
  trials = 12,
  nplayers = 5, # number of players per session
  durations.vec = c(75, 90, 105)  # The simulation functions sample trial lengths from this vector (equally) 
                                  # and randomly assigns them to the different environments
)
# Add unique ids for players (rows are sessions)
exp.pars$id = with(exp.pars, matrix(1:(sessions*nplayers), ncol=nplayers, byrow = T))

# Environmental parameters (identical for all simulations)
max = c(.5, .7, .9)
ratio = c(.5, .65, .8, .95)
env.pars = expand.grid(max=max, ratio=ratio)
env.pars = list(max=env.pars$max, ratio=env.pars$ratio)

```

## MCMC
Models were estimated with the following MCMC settings.
```{r, mcmc-asoc-parrecov, echo=T}
# MCMC
chains = 4
cores = 4
iter = 2000
warmup = 1000
refresh = 100
```


## Parameter Recovery


The following code shows how the parameter recovery was computed
```{r, asoc-parrecov, echo=T, results='markup', fig.width=24, fig.height=13.5}
if(!exists(paste("asocial/results/parrecov", paste(models$name[[mod]], "Rdata", sep = "."), sep = "/"))){
  
  # Results list
  results = list()
  
  # Get simulation function for model
  f = get(models$sim[[mod]])
  
  # Generate sobol sequence
  rl.pars = sobol(n = nsim, dim = length(models$free.pars[[mod]]), init = T)
  
  # Rescale to parameter range
  rl.pars = sapply(1:ncol(rl.pars), function(x)
    models$free.pars[[mod]][[x]][[1]] + 
        (models$free.pars[[mod]][[x]][[2]] - models$free.pars[[mod]][[x]][[1]]) * rl.pars[, x]
    ) 
  
  # Account for different variable types when nsim == 1 or > 1
  if(nsim == 1){rl.pars = t(rl.pars)}else{rl.pars = rl.pars}
  
  # Rename
  rl.pars = rl.pars %>%
    as.data.frame() %>% 
    `colnames<-`(names(models$free.pars[[mod]])) %>%
    cbind(models$fixed.pars[[mod]])
    
  # Loop over simulations
  for(sim in 1:nsim){
  
    # Write log to text file fot when knitting
    prgrss = paste("Simulating from model", models$name[[mod]], ". Simulation", sim, "out of", nsim)
    log.file = paste(paste("asocial/results/parrecov",
                                    "log.txt", sep = "/"))
    if(!file.exists(log.file)){file.create(log.file)}
    write(prgrss, log.file, append = TRUE, ncolumns = 1)
    
    # Check if there are any nested parameters
      if(any(sapply(models$free.pars.struct[[mod]], function(x) is.list(x)))){
        
        # Get nested lists in models free pars (pars with offsets)
        indx = sapply(models$free.pars.struct[[mod]], function(x) is.list(x))
        indx = indx[indx == TRUE]
        
        # "Unpack" nested list index to index rl.pars data frame
        indx.df = lapply(names(indx), function(x) grepl(x, names(rl.pars)))
        names(indx.df) = names(indx)
        
        
        # Get rl.pars and add to sim pars
        sim.pars = c(exp.pars, env.pars,
                     lapply(indx.df, function(x) matrix(data = rl.pars[sim, x], nrow = length(unique(max)))), # nested pars
                     rl.pars[sim, which(!apply(as.data.frame(indx.df), 1, any))] # non-nested pars
        )
        
        # Unlist individual learning rates
        if(models$name[[mod]] != "m4.3"){
          sim.pars$alphaQN = unlist(sim.pars$alphaQN)
          sim.pars$alphaQP = unlist(sim.pars$alphaQP)
        }
      }else{
        # Get rl.pars and add to sim pars
        sim.pars = c(exp.pars, env.pars, rl.pars[sim, ])
      }
    
    # Simulate data
    sim.data = f(sim.parameters = sim.pars)
  
    # Put data in list
    stan.data = with(sim.data, list(
      OBSERVATIONS=nrow(sim.data),
      SESSIONS=max(unique(session)), session=session,
      TRIALS=max(unique(trial)), trial=trial,
      MAXIMUM=length(unique(max.fac)), maximum=max.fac,
      RATIO=length(unique(ratio.fac)), ratio=ratio.fac,
      PLAYERS=unique(nplayers),
      TIMES=max(unique(time)), time=time,
      DECISIONS=length(unique(decision)), decision=decision, 
      REWARDS=length(unique(reward)), reward=reward
    ))
    
    # Fit model
    fit = stan(file = models$stan[[mod]], data = stan.data,
               chains = chains, cores = cores, iter = iter, warmup = warmup, refresh = refresh)
    
    # Plot and save some diagnostics
    diag.list = diag.plot(model.fit = fit, plot.pars = names(models$free.pars[[mod]]))
    ggexport(plotlist = diag.list, width = 1920, height = 1080,
             filename = paste("asocial/results/parrecov/diagnostics", paste(models$name[[mod]], "sim", sim, "diagnostics", "jpeg",  sep = "."), sep = "/"))
    
    
    # Summarise posterior
    # Get generating parameters
    true.pars = rl.pars[sim, names(models$free.pars[[mod]])] %>% 
      pivot_longer(everything(), names_to = "par", values_to = "true.pars")
    
    fit.sum = fit %>% 
      tidy_draws() %>%
      select(names(models$free.pars[[mod]])) %>%
      pivot_longer(everything(), names_to = "par", values_to = ".mean") %>%
      group_by(par) %>%
      mean_hdci() %>%
      left_join(., true.pars, by = join_by(par)) %>%
      mutate(sim = sim)
      
  
    # Add to results list
    results[[sim]] = fit.sum
    
    
  }
  
  # Plot results for model we just simulated from
  results = bind_rows(results) %>% 
    mutate(par = factor(par, levels = names(models$free.pars[[mod]]))) # factorise for ordering when plotting
  
  # Save results for model 
  save(results, file = paste("asocial/results/parrecov", paste(models$name[[mod]], "Rdata", sep = "."), sep = "/"))


}else{
    
  # Save results for model 
  load(file = paste("asocial/results/parrecov", paste(models$name[[mod]], "Rdata", sep = "."), sep = "/"))

}

p = plot.par.recov(model.name = models$name[[mod]],
                     results = results, plot.pars = names(models$free.pars[[mod]]))
  ggexport(p, width = 2560, height = 1440,
           filename = paste("asocial/results/parrecov", paste(models$name[[mod]], "jpeg", sep = "."), sep = "/"))
print(p)




```